A Survey of Current Exoskeletons\\ and Their Control Architectures and Algorithms\\ (Draft 3.2)

### 2015-09-30 exos/exosText_dualMode.tex
complete version of survey.tex

The Hydraulic Lower Extremity Exoskeleton's actuators were designed based on human walking data obtained at 4km/h with a 45 kg load.  Based on this data, the hydraulic capacity system was designed to provide 2050psi and 8lpm.  The individual actuators were designed to be double acting at the hip and knee flexion/extension joints. They provide a {\bf hip maximum thrust of 4 kN} and {\bf knee maximum thrust of 4 kN}.  Each joint joint includes three-way servo valves (M 200, Star-Hydraulic) to control rate and direction of bi-directionality, and bypass valves to connect the pump path to tank path for fast, energy-efficient motion during swing phases.

@@

The mechanical as well as control design of the Hydraulic Lower Extremity Exoskeleton was straight-forward and contained many aspects which we support.  In particualr, we supported the use of off-the-shelf components in the hardware design and the addition of bypass valves to take advantage of passive dynamics during walking to produce more energy conscious behaviors.

@@

One potential drawback of this hardware is the power system.  The documentation in \cite{dual_mode_2014} was sparse with respect to the exact specifications of the motor and energy storage device which powers the hydraulic system.  Additionally, in the long-term control design strategy, pure get out of the way control using measurements of the suit only has drawbacks, as mentioned previously.  This strategy will ultimately lead to a ``sensitivity amplification" -like behavior.  This strategy will thus be positively sensitive to user intended motion and negatively sensitive to external disturbances.

>>>>

The Hydraulic Lower Extremity Exoskeleton's actuators were designed based on human walking data obtained at 4 km/h with a 45 kg load.  Based on this data, the hydraulic capacity system was designed to provide 2050 psi and 8 LPM.  The individual actuators were designed to be double acting at the hip and knee flexion/extension joints. They provide a {\bf hip maximum thrust of 4 kN} and {\bf knee maximum thrust of 4 kN}.  Each joint joint includes three-way servo valves (M 200, Star-Hydraulic) to control rate and direction of bi-directionality, and bypass valves to connect the pump path to tank path for fast, energy-efficient motion during swing phases.

@@

The mechanical as well as control design of the Hydraulic Lower Extremity Exoskeleton was straight-forward and contained many aspects which we support.  In particular, we supported the use of off-the-shelf components in the hardware design and the addition of bypass valves to take advantage of passive dynamics during walking to produce more energy conscious behaviors.

@@

One potential drawback of this hardware is the power system.  The documentation in \cite{dual_mode_2015} was sparse with respect to the exact specifications of the motor and energy storage device which powers the hydraulic system.  Additionally, in the long-term control design strategy, pure get out of the way control using measurements of the suit only has drawbacks, as mentioned previously.  This strategy will ultimately lead to a ``sensitivity amplification" -like behavior.  This strategy will thus be positively sensitive to user intended motion and negatively sensitive to external disturbances.

### 2015-09-30 exos/hal.tex
complete version of survey.tex

The hybrid assistive limb (HAL) exoskeleton is developed by the University of Tsukuba and Cyberdyne for human strength augmentation and as an assistive gait device in rehabilitation.  Although several prototypes have been developed, this section focuses on the most recent HAL-5 model (specifically the non-clicial type, HAL-5 Type-B). Though HAL-5 is a full body exoskeleton, only hip, knee joints, and ankle are actuated in the sagittal plane.  The exoskeleton uses DC motors with harmonic drives at hip, knee, ankle joints (in some models the ankle joints act as passive springs).  HAL weighs 23kg and includes an on-board AC100V battery as the power source, which is designed to support maximum velocity human walking and standing torque requirements.  The battery allows for 160 min of continuous operation and enables the exoskeleton to lift up to 70kg \cite{HALassist2011}.

>>>>

The hybrid assistive limb (HAL) exoskeleton is developed by the University of Tsukuba and Cyberdyne for human strength augmentation and as an assistive gait device in rehabilitation.  Although several prototypes have been developed, this section focuses on the most recent HAL-5 model (specifically the non-clinical type, HAL-5 Type-B). Though HAL-5 is a full body exoskeleton, only hip, knee joints, and ankle are actuated in the sagittal plane.  The exoskeleton uses DC motors with harmonic drives at hip, knee, ankle joints (in some models the ankle joints act as passive springs).  HAL weighs 23kg and includes an on-board AC100V battery as the power source, which is designed to support maximum velocity human walking and standing torque requirements.  The battery allows for 160 min of continuous operation and enables the exoskeleton to lift up to 70kg \cite{HALassist2011}.
